Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-30 prop_letter.tex
prop_letter.tex \paragraph{Contextuality Inequality} Type something...

Cabello proved some inequalities to verify contextuality~\cite{Cabello_2008},
and we want to adopt these inequalities into our setting.

First, although his inequality (4) bases on Mermin square and looks
simple, we cannot use it directly because they are not projectors.
Instead $A_{ij}$ in his equation (1) are almost projectors, because
$A_{ij}=2\proj{v_{ij}}-\mathbb{1}$, and $\ket{v_{ij}}$ are eigenstates
of Mermin square. It is easier to write an inequality start from equation
(1).

>>>>

Although Cabello proved some inequalities to verify contextuality~\cite{Cabello_2008},
it seems not directly relating to empty/non-empty core. On one hand,
the part using hidden variables cannot really apply on quantum IVPM
expect $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
case discussed in the Kochen-Specker theorem paragraph. On the other
hand, for the part predicted by quantum mechanics, the product of
observables in inequalities are always either $\mathbb{1}$ or $-\mathbb{1}$
whose the interval-valued probabilities and expectation values are
always $\necess$. In these kind of situation, the inequalities applies
on all IVPMs, no matter whether it has an empty or non-empty core.
